Cover Times of Random Walks

### 2019-04-11 paper.tex
electrical network section

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{varioref}
\usepackage{verbatim} 
\usepackage{multicol}
\usepackage{enumerate}
\usepackage[normalem]{ulem}
%\usepackage[margin=1in]{geometry}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{thm-restate}
\usepackage{enumitem}

%\usepackage{cite}
\usepackage{cite}

@@

\DeclareMathOperator{\E}{\mathrm{E}}		% expected value
\DeclareMathOperator{\pr}{\mathrm{P}}		% expected value
\DeclareMathOperator{\cov}{t_\textrm{cov}}  % cover time
\DeclareMathOperator{\hit}{t_{\textrm{hit}}}% hitting time

@@

We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ in $E(G)$.
Let $c(i,j)$ be the non-negative weight of the edge between vertices $i$ and $j$.
If the graph is unweighted then $c(i,j) = 1$ if $i \sim j$.

Define the weight of vertex $i$ 
\begin{align}
c(i) &= \sum_{j:i \sim j} c(i,j). \nonumber
\end{align}

We consider a random walk $(X_t)$ on $G$.
Call $X_t$ the vertex that the walk is on at time $t$.
The random walker begins at vertex $X_0$.
At each step, the walker at vertex $i$ moves to neighboring vertex
$j$ with probability $\frac{c(i,j)}{c(i)}$.

Let $T_{j}$ be the number of steps until the first visit to $j$.
Formally,
\begin{align}
T_{j} &= \textrm{min} \left\{t : X_t = j \right\}. \nonumber
\end{align}
Let the hitting time $\hit$ be the maximum expected time between two vertices on $G$.
Formally, 
\begin{align}
\hit &= \max_{i,j \in V(G)} \E_i[T_j]. \nonumber
\end{align}
Note that $\E_i[T_j] = \E[T_j | X_0 = i]$.
Let the cover time be the time until all vertices have been
visited by the random walk $(X_t)$.
We typically refer to the expected cover time $\cov$.
Formally,
\begin{align}
\cov &= \E [ \max_{j \in V(G)} T_j ]. \nonumber
\end{align}

@@

For a graph with $n$ vertices, there are $n$ possible choices for the current
vertex and $2^{n-1}$ possible combinations of visited and unvisited vertices
for each one.
Of course, some states are inaccessible.
But even on \cref{fig:example} where we exploit symmetry,
there are almost a prohibitive number of cases.
It is easy to see that the number of states
grows exponentially with the number of vertices.

@@

				    \node (l) at (.5, 1.1) {$\cov$};

@@

	\caption{First step analysis applied to a small, asymmetric graph with $n=4$.}\label{fig:example}

@@

If we let the label of each graph in \cref{fig:example}
denote the expected cover time from that graph, we have the following system
of equations:
\begin{align}
\cov &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} \nonumber \\
\textrm{a} &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{c} \nonumber \\
\textrm{b} &= 1 + \frac{1}{2}\textrm{b} + \frac{1}{2}\textrm{e} \nonumber \\
\textrm{c} &= 1 + 1\textrm{e} \nonumber\\
\textrm{d} &= 1 + \frac{1}{3}\textrm{a} + \frac{1}{3}\textrm{e} + \frac{1}{3}\textrm{f} \nonumber \\
\textrm{e} &= 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3}\dot 0\nonumber \\
\textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2}\dot 0\nonumber \\
\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber
\end{align}

With a little linear algebra, we find that $\cov = \frac{43}{6}$.

For large graphs, the first step analysis as an approach to finding the expected
cover time is obviously intractable.
The rest of this section deals with particularly symmetric graphs
for which it is possible find a solution for an arbitrary $n$.
However, we must rely on expected cover time bounds for the vast majority of cases.

@@

Our goal is to find the expected number of steps until we have visited all
$n$ vertices in the complete graph.
Observe that the random walk can start at any vertex without loss of generality
because the graph is symmetric.
The strategy is to write the cover time $\cov$ in terms of the expected
value of more simple random variables.
Let $X_i$ be the random variable that represents the number of steps to go
from $i-1$ to $i$ unique vertices (excluding the current vertex).

We write the cover time in terms of $X_i$ and use linearity of expectation.
\begin{align}
\cov&= \E[X_1+X_2+X_3+...+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
\end{align}

The random variable $X_i$ takes value $k$ when $k-1$ steps lead us to
already visited vertices and the $k^{th}$ step is to a previously unvisited vertex.
It follows that $X_i$ is geometric with distribution
\begin{align}
\pr(X_i = k) = (1-p_i)^{k-1}p_i, \nonumber
\end{align}
where $p_i$ is the probability of moving to a previously unvisited vertex.
Then $\E[X_i] = \frac{1}{p_i}$. We now find the probability $p_i$ that 
we go to a previously unvisited vertex is $\frac{n-i}{n-1}$.
This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
It follows that $\E[X_i] = \frac{n-1}{n-i}$.
Then
\begin{align}
\cov&=   \sum_{i=1}^n \frac{n-1}{n-i} \nonumber \\
&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
\end{align}

A natural interpretation of the cover time on a complete graph is 
the so-called coupon collecting problem.
There are $r$ different coupons that are randomly packaged in cereal boxes.
An avid fan buys a box of cereal every day.
We want to know how many days until the fan has collected each coupon.
The strategy is to think of every coupon as a vertex on the complete graph.
We then move from vertex to vertex with uniform probability.
The difference between the coupon collecting problem and the complete graph
is that we now have self-edges.
Before, we had to leave our current vertex at each step.
Now, we can stay in the same vertex (provided our collector found the same coupon
two days in a row).
We apply our approach to the complete graph and substitute the $r$ possible coupons
we can find for the $n-1$ vertices we could move to.
Then
\begin{align}
\cov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+...+1\right). \nonumber
\end{align}

@@

An $n$-star is a graph with one central vertex and $n-1$ adjacent vertices each with a single
edge to the center.
A random walk begins at the central vertex and moves with uniform probability to
one of the $n-1$ adjacent vertices.
Whereas in the complete graph and coupon collecting problems we 
restarted in one step, a random walk on the $n$-star probabilistically restarts
in two steps: one step to each leaf and one step back.
We apply our approach to the complete graph and conclude that

\begin{align}
\cov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
\end{align}

@@

\begin{align}
\left(e_{2} - e_1\right) &= \left(e_1 - e_{0}\right) - 2 \nonumber \\
\left(e_{3} - e_2\right) &= \left(e_2 - e_{1}\right) - 2 = \left(e_1 - e_{0}\right) - 4\nonumber \\
\left(e_{4} - e_3\right) &= \left(e_3 - e_{2}\right) - 2 = \left(e_1 - e_{0}\right) - 6\nonumber \\
&\;\;\vdots \nonumber\\
\left(e_N - e_{N-1}\right) &= \left(e_1 - e_0\right) - 2 (N-1) \nonumber \\
\left(0 - e_1\right) &= \left(e_1 - 0\right) - 2 (N-1) \nonumber \\
e_1 &= N-1. \nonumber
\end{align}

@@

\begin{align}
e_2  &= e_1 + (e_1 - e_0) - 2 = 2 (N - 2) \nonumber\\
e_3  &= e_2 + (e_2 - e_1) - 2 = 2 \left[2 (N-2) \right] - (N-1) -2 = 3 (N - 3) \nonumber\\
&\;\;\vdots \nonumber\\
e_i &= i (N-i) \label{eq:line}
\end{align}

@@

Then, by \cref{thm:line}, for the random walk from state $i$ on the line graph,
\begin{align}
\cov = i(N-i) + N^2. \nonumber
\end{align}

@@

Consider a random walk on a simple cycle as in \cref{fig:cycle}.
(Note that the starting vertex is arbitrary since the graph is symmetric.)
Let $(X_t)$ be the walk on the number line (between $-n$ and $n$)
where $X_0 = 0$.
The cover time $\cov$ of the simple cycle is the expected number of steps 
until we visit $n$ distinct integers.

@@

Let $\{a, a+1, \dots, b-1, b\}$ 
denote the set of vertices we have visited.
Since the walk is on a line, we can write $[a,b]$ for the range
of the walk where $a$ is the smallest 
and $b$ is the largest vertex we have visited.
Notice that if $a \leq -n$ or $b \geq n$, we have covered all $n$ vertices
on the simple cycle and conclude the random walk.

In a slight abuse of notation, let $T_k$ be the 
number of steps until we reach $k$ distinct vertices.
Formally, $T_k = \min\{t: b-a+1 = k\}$.
Then by telescoping,
\begin{align}
\cov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \dots + 
(T_k - T_{k-1}) + \dots + (T_n - T_{n-1})] \nonumber
\end{align}

At time $T_{k}$, we are either at integer $a$ or $b$.
Then $\E[T_{k+1}-T_{k}]$ is the expected time until we reach $a-1$ or $b+1$.
Notice that we can shift our endpoints to 0 and $b+1-(a-1) = b-a + 2 = k+1$.
The expected number of steps to either $a-1$ or $b+1$
is $1\dot (k+1-1) = k$ by \cref{thm:line}.

By linearity of expectation,
\begin{align}
\cov &=  (\E[T_2] - \E[T_1]) + \dots +
(\E[T_{k+1}] - \E[T_{k}]) + \dots + (\E[T_n] - \E[T_{n-1}]) \nonumber\\
&= 1 + 2 + \dots + k-1 + \dots + n-1  = \frac{1}{2}n(n-1). \nonumber
\end{align}

\section{Bounds}
\subsection{Matthews Method}
We have seen that it is in general very hard
to calculate the expected cover time of a random walk
on a graph.
The exceptions are symmetric or small graphs.
In lieu of an exact solution, we want to 
bound the expected cover time.

@@

\begin{theorem}
Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews}
\end{theorem}
\begin{align}
\cov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + ... + \frac{1}{n-1} \right). \nonumber
\end{align}

@@

Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, ..., \sigma_k$
have all been visited.
For ease of notation, set $L_k = X_{T_k}$ to be the last state among 
$\sigma_1, \sigma_2, ..., \sigma_k$ to be visited (the first
time they are all visited).

We begin by writing the expected cover time in a clever way
(similar to the strategy we employed on the cycle graph):
\begin{align}
\cov &= \E_n[{T_{n-1}}]  \nonumber \\
&= \E_n[T_1 + (T_2 - T_1) + ... + 
(T_k - T_{k-1}) + ... + (T_{n-1} - T_{n-2})] . \nonumber
\end{align}

@@

Since $\sigma$ is a random permutation, the probability that
we visit $\sigma_k$ last is $\frac{1}{k}$.
Formally, $P(L_k = \sigma_k) = \frac{1}{k}$.

@@

Putting it all together,
\begin{align}
\cov \leq \hit \left( 1+ \frac{1}{2} + ... + \frac{1}{k} 
+ ... + \frac{1}{n-1} \right). \nonumber
\end{align}

@@

@@

\section{Electrical Networks}
\subsection{Definitions}
\cite{AF14} 3.3
\subsection{Commute Time}
\cite{AF14} Proposition 2.3 -> Corollary 2.8 -> Corollary 3.11

\url{https://ocw.mit.edu/courses/mathematics/18-445-introduction-to-stochastic-processes-spring-2015/lecture-notes/MIT18_445S15_lecture8.pdf}

\subsection{Balanced Trees}
\cite{LP17} 11.3

@@

\cite{AF14}
\cite{Bo98}
\cite{DS84}
\cite{Du11}
\cite{Gr10}
\cite{LP17}

>>>>

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{varioref}
\usepackage{verbatim} 
\usepackage{multicol}
\usepackage{enumerate}
\usepackage[normalem]{ulem}
%\usepackage[margin=1in]{geometry}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage{thm-restate}
\usepackage{enumitem}
\usepackage{upgreek}
%\usepackage{cite}
\usepackage{cite}

@@

\DeclareMathOperator{\E}{\mathrm{E}}		     % expected value
\DeclareMathOperator{\pr}{\mathrm{P}}		     % expected value
\DeclareMathOperator{\cov}{\uptau_\textrm{cov}}  % cover time variable
\DeclareMathOperator{\tcov}{t_\textrm{cov}}      % cover time
\DeclareMathOperator{\hit}{t_{\textrm{hit}}}     % hitting time
\DeclareMathOperator{\Ceff}{C_\textrm{eff}}      % effective conductance
\DeclareMathOperator{\Reff}{R_{\textrm{eff}}}     % effective resistance

@@

We say $i\sim j$ for $i$ and $j$ in the vertex set $V(G)$ if $(i,j)$ in $E(G)$.
Let $C_{i,j}$ be the non-negative weight of the edge between vertices $i$ and $j$.
We will mostly consider unweighted graphs
with $C_{i,j} = 1$ if $i \sim j$ and $C_{i,j} = 0$ otherwise.

Define the weight of vertex $i$ 
\begin{align}
C_i &= \sum_{j:i \sim j} C_{i,j}. \nonumber
\end{align}
In the unweighted case, $C_i$ is the degree of vertex $i$.

We consider a random walk $(X_t)$ on $G$.
Call $X_t$ the vertex that the walk is on at time $t$.
The random walker begins at vertex $X_0$.
At each step, the walker at vertex $i$ moves to neighboring vertex
$j$ with probability $c(i,j)/c(i)$.

Let $T_{j}$ be the number of steps until the first visit to $j$.
Formally,
\begin{align}
T_{j} &= \textrm{min} \left\{t > 0 : X_t = j \right\}. \nonumber
\end{align}
Let the hitting time $\hit$ be the maximum expected time between two vertices on $G$.
Note that $\E_i[T_j] = \E[T_j | X_0 = i]$.
Formally, 
\begin{align}
\hit &= \max_{i,j \in V(G)} \E_i[T_j]. \nonumber
\end{align}
Let the cover time variable $\cov$ be the first time all vertices have been
visited by the random walk $(X_t)$.
Formally, $\cov$ is the minimum time that for all $i \in V(G)$
there exists $t \leq \cov$ such that $X_t = i$.
We also define the cover time as the expected value of $\cov$ from
the worst initial vertex.
Formally,
\begin{align}
\tcov &= \max_{j \in V(G)} \E_j[\cov] . \nonumber
\end{align}

@@

For a graph with $n$ vertices, there are $n$ possible choices for the current
vertex and $2^{n-1}$ possible combinations of visited and unvisited vertices
for each one.
Of course, some cases are inaccessible by a random walk.
But even on \cref{fig:example} where we exploit symmetry,
there are almost a prohibitive number.
It is easy to see that the number of cases 
grows exponentially with the number of vertices.

@@

				    \node (l) at (.5, 1.1) {$\tcov$};

@@

	\caption{First step analysis applied to a small graph with $n=4$.}\label{fig:example}

@@

If we let the label of each graph in \cref{fig:example}
denote the cover time from that case, we have the following system
of equations:
\begin{align}
\tcov &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{b} \nonumber \\
\textrm{a} &= 1 + \frac{1}{3}\textrm{a} + \frac{2}{3}\textrm{c} \nonumber \\
\textrm{b} &= 1 + \frac{1}{2}\textrm{b} + \frac{1}{2}\textrm{e} \nonumber \\
\textrm{c} &= 1 + 1\textrm{e} \nonumber\\
\textrm{d} &= 1 + \frac{1}{3}\textrm{a} + \frac{1}{3}\textrm{e} + \frac{1}{3}\textrm{f} \nonumber \\
\textrm{e} &= 1 + \frac{1}{3}\textrm{c} + \frac{1}{3}\textrm{e} + \frac{1}{3}\dot 0\nonumber \\
\textrm{f} &= 1 + \frac{1}{2}\textrm{g} + \frac{1}{2}\dot 0\nonumber \\
\textrm{g} &= 1 + \frac{2}{3}\textrm{f} + \frac{1}{3}\dot 0\nonumber
\end{align}

With a little linear algebra, we find that $\tcov = 43/6$.

For large graphs, the first step analysis as an approach to finding the expected
cover time is obviously intractable.
The rest of this section deals with particularly symmetric graphs
for which it is possible to find a solution for an arbitrary $n$.
However, we must rely on cover time bounds for the vast majority of cases.

@@

Our goal is to find the expected number of steps until we have visited all
$n$ vertices in the complete graph.
Observe that the random walk can start at any vertex without loss of generality
because the graph is symmetric.
The strategy is to write the cover time $\tcov$ in terms of the expected
value of more simple random variables.
Let $X_i$ be the random variable that represents the number of steps to go
from $i-1$ to $i$ unique vertices (excluding the current vertex).

We write the cover time in terms of $X_i$ and use linearity of expectation.
\begin{align}
\tcov&= \E[X_1+X_2+X_3+...+X_{n+1}] = \sum_{i=1}^n \E[X_i] \nonumber
\end{align}

The random variable $X_i$ takes value $k$ when $k-1$ steps lead us to
already visited vertices and the $k^{th}$ step is to a previously unvisited vertex.
Then $X_i$ is certainly geometric and $\E[X_i] = 1/p_i$.

\begin{comment}
It follows that $X_i$ is geometric with distribution
\begin{align}
\pr(X_i = k) = (1-p_i)^{k-1}p_i, \nonumber
\end{align}
where $p_i$ is the probability of moving to a previously unvisited vertex.
\end{comment}
We now find the probability $p_i$ that 
we go to a previously unvisited vertex is $(n-i)/(n-1)$.
This is because there are $n-i$ unvisited vertices and a total of $n-1$ adjacent vertices.
It follows that $\E[X_i] = (ln-1)(n-i)$.
Then
\begin{align}
\tcov&=   \sum_{i=1}^n \frac{n-1}{n-i} \nonumber \\
&=  (n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
\end{align}

A natural interpretation of the cover time on a complete graph is 
the so-called coupon collecting problem.
There are $r$ different coupons that are randomly packaged in cereal boxes.
An avid fan buys a box of cereal every day.
We want to know how many days until the fan has collected each coupon.
The strategy is to think of every coupon as a vertex on the complete graph.
We then move from vertex to vertex with uniform probability.
The difference between the coupon collecting problem and the complete graph
is that we now have self-edges.
Before, we had to leave our current vertex at each step.
Now, we can stay in the same vertex (provided our collector found the same coupon
two days in a row).
We apply our approach to the complete graph and substitute the $r$ possible coupons
we can find for the $n-1$ vertices we could move to.
Then
\begin{align}
\tcov&=  r \left(\frac{1}{r}+\frac{1}{r-1}+...+1\right). \nonumber
\end{align}

@@

An $n$-star is a graph with one central vertex and $n-1$ adjacent vertices each with a single
edge to the center.
A random walk begins at the central vertex and moves with uniform probability to
one of the $n-1$ adjacent vertices.
Whereas in the complete graph and coupon collecting problems we 
visited a (possibly) new vertex in one step,
a random walk on the $n$-star visits a (possibly) new vertex
in two steps: one step to each leaf and one step back.
We apply our approach to the complete graph and conclude that

\begin{align}
\tcov&= 2(n-1) \left(\frac{1}{n-1}+\frac{1}{n-2}+...+1\right). \nonumber
\end{align}

@@

\begin{align}
(e_2 - e_1) &= (e_1-e_0) -2 \nonumber\\
(e_3 - e_2) &= (e_1-e_0) -4 \nonumber\\
&\;\;\vdots \nonumber\\
\left(e_N - e_{N-1}\right) &= \left(e_1 - e_0\right) - 2 (N-1) \nonumber \\
\left(0 - e_1\right) &= \left(e_1 - 0\right) - 2 (N-1) \nonumber \\
e_1 &= N-1. \nonumber
\end{align}

@@

\begin{comment}
\begin{align}
e_2  &= e_1 + (e_1 - e_0) - 2 = 2 (N - 2) \nonumber\\
e_3  &= e_2 + (e_2 - e_1) - 2 = 2 \left[2 (N-2) \right] - (N-1) -2 = 3 (N - 3) \nonumber\\
&\;\;\vdots \nonumber\\
e_i &= i (N-i) \label{eq:line}
\end{align}
\end{comment}

\begin{align}
(e_2 - e_1) &= (e_1-e_0) -2 \nonumber\\
(e_3 - e_2) &= (e_1-e_0) -4 \nonumber\\
&\;\;\vdots \nonumber\\
(e_i-e_{i-1}) &= (e_1 - e_0) - 2(i-1) \nonumber
\end{align}

Remember that $e_0=0$, $e_1=N-1$, and 
$\sum_{i}^{i-1} i = (i-1)i/2$.
We add all $i-1$ equations:

\begin{align}
(e_i - e_1) &= (i-1) e_1 - 2[1+2+...+i-1] \nonumber \\
e_i &= i(N-1) - 2 \frac{(i-1)i}{2} \nonumber\\
&= i(N-1 - i + 1) = i(N-i)
\label{eq:line}
\end{align}

@@

Then, by \cref{thm:line}, for the random walk from state $i$ on the line graph,
\begin{align}
\tcov = i(N-i) + N^2. \nonumber
\end{align}

@@

Consider a random walk on a simple cycle as in \cref{fig:cycle}.
(Note that the starting vertex is arbitrary since the graph is symmetric.)
Let $(X_t)$ be the walk on the number line (between $-n$ and $n$)
where $X_0 = 0$.
The cover time $\tcov$ of the simple cycle is the expected number of steps 
until we visit $n$ distinct integers.

@@

Let $\{a, a+1, \dots, b-1, b\}$ 
denote the set of vertices we have visited.
Since the walk is on a line, we can $[a,b]$ for the range
of the walk where $a$ is the smallest 
and $b$ is the largest vertex we have visited.
Notice that if $a \leq -n$ or $b \geq n$, we have covered all $n$ vertices
on the simple cycle and conclude the random walk.

In a slight abuse of notation, let $T_k$ be the 
number of steps until we reach $k$ distinct vertices.
Formally, $T_k = \min\{t: b-a+1 = k\}$.
Then by telescoping,
\begin{align}
\tcov &= \E[T_n] = \E[(T_2 - T_1) + (T_3 - T_2) + \dots + 
(T_k - T_{k-1}) + \dots + (T_n - T_{n-1})] \nonumber
\end{align}

At time $T_{k}$, we are either at integer $a$ or $b$.
Then $\E[T_{k+1}-T_{k}]$ is the first time we reach $a-1$ or $b+1$.
Notice that we can shift our endpoints to 0 and $b+1-(a-1) = b-a + 2 = k+1$.
The expected number of steps to either $a-1$ or $b+1$
is $1\dot (k+1-1) = k$ by \cref{thm:line}.

By linearity of expectation,
\begin{align}
\tcov &=  (\E[T_2] - \E[T_1]) + \dots +
(\E[T_{k+1}] - \E[T_{k}]) + \dots + (\E[T_n] - \E[T_{n-1}]) \nonumber\\
&= 1 + 2 + \dots + k-1 + \dots + n-1  = \frac{1}{2}n(n-1). \nonumber
\end{align}

\section{Electrical Networks}
\cite{DS84}
There are many connections between electrical networks
and random walks.
Physical properties like voltage, current, and resistance
all have probabilistic interpretations.
In this section, we explore electrical networks to build intuition about 
random walks and motivate a result we use to bound cover times.

So that the reader may more easily distinguish between
vertices, consider $x$ and $y$ in $V(G)$.
Recall that $C_{x,y}$ is the weight of the edge
between vertices $x$ and $y$, $C_x$ is the sum
of all $C_{x,y}$ where $x \sim y$, and the probability $\pr_{x,y}$
that we go from $x$ to $y$ is $C_{x,y}/C_x$.
For the rest of this section, we will call $C_{x,y}$
the conductance between $x$ and $y$.
Define the resistance $R_{x,y}$ between $x$ and $y$
as $1/ C_{x,y}$.

We now consider the distribution of the random
walk on the vertices of our graph.
Define the proportion $\pi_x$ of time we spend in $x$
as $C_x/C$ where $C=\sum_y C_y$.

We verify that $\pi$ is the stationary distribution
of $(X_t)$.
To begin,
\begin{align}
C_x \pr_{x,y} &= C_x \frac{C_{x,y}}{C_x} = C_{x,y} = C_{y,x} 
= C_y \frac{C_{y,x}}{C_y} = C_y \pr_{y,x}. \nonumber
\end{align}
Dividing by $C$ gives $\pi_x \pr_{x,y} = \pi_y \pr_{y,x}$.
(So $\pi$ satisfies detailed balance.)
Summing over $x$,
\begin{align}
\sum_x \pi_x \pr_{x,y} = \pi_y . \nonumber
\end{align}
Then $\pi \pr = \pi$ where $\pr$ is the matrix of transition probabilities.
It follows that $\pi$ is indeed the stationary distribution of $(X_t)$.

We now introduce voltage, current, and effective resistance.
Consider $a$ and $b$ in $V(G)$.
Set the voltage to be 1 at $a$ and 0 at $b$.
We may think of voltage as the probability we get to $a$ before $b$.
Probabilistically, of course $v_a = 1$ and $v_b=0$.
Voltage is a harmonic function so the voltage at every vertex $x$ in 
$V(G) \textbackslash \{a,b\}$ is determined by the boundary values
(at $a$ and $b$).

The current between two vertices is the product of the
difference in their voltages and the conductance of their edge.
We may think of current as the net number of movements through an edge.
Kirchoff's Current Law says that the sum of current on any vertex is 0.
Probabilistically, of course every time we enter a vertex we must also leave it.
Using Kirchoff's Current Law and the definition of current,
we justify the probabilistic interpretation of voltage
\begin{align}
\sum_y i_{x,y} &= 0 = \sum_y (v_x - v_y)C_{x,y} \nonumber \\
v_x \sum_y C_{x,y} &= \sum_y C_{x,y} v_y \nonumber \\
v_x &= \sum_y \frac{C_{x,y}}{C_x} v_y = \sum_y \pr_{x,y} v_y. \nonumber
\end{align}
We can probabilistically verify that $v_x = \sum_y \pr_{x,y} v_y$
using first step analysis on the probability of reaching $a$ before $b$.

We now have the requisite background to prove a result
we will use to bound cover times.
Define the probability $\pr_a(T_b < T_a)$ that starting at $a$
we reach $b$ before returning to $a$.
(Recall that $T_a>0$.)
Now define the effective conductance $\Ceff$ as $i_a/v_a$.

With a voltage of 1 at $a$ and 0 at $b$,
\begin{align}
\Ceff &= i_a/1 =
\sum_y (v_a - v_y) C_{a,y} =
\sum_y (v_a - v_y) \frac{C_{a,y}}{C_a} C_a \nonumber \\
&= C_a (\frac{v_a}{C_a} \sum_y C_{a,y} - \sum_y \frac{C_{a,y}}{C_a} v_y)=
C_a(1-\sum_y\pr_{a,y}v_y).\nonumber
\end{align}

Recall $\sum_y P_{a,y} v_y$ is the probability we reach $a$ before $b$
so 1 minus that is the probability we reach $b$ before returning to $a$.

Then
\begin{align}
\Ceff = C_a \pr_a(T_b < T_a) \nonumber
\end{align}
and
\begin{align}
\Reff = \frac{1}{C_a \pr_a(T_b < T_a)}. \nonumber
\end{align}

We use the fact that $\pi_a = C_a / C$ and multiply by $C$,
\begin{align}
\Reff C = \frac{1}{\pi_a \pr_a(T_b < T_a)}. \nonumber
\end{align}

Now our job is to interpret $\Reff C$.
Recall that $\pr_a(T_b < T_a)$ is the probability, starting from $a$,
that we get to $b$ before returning to $a$.
We do independent trials, starting from $a$, until we reach $b$ before $a$.
Each ``failure'' resets the process so $\pr_a(T_b < T_a)$ is geometrically distributed.
Then the expected value $1/\pr_a(T_b < T_a)$ is the expected number of times
we return to $a$ before we finally reach $b$ (and again return to $a$).

Recall that $\pi_a$ is the probability that $(X_t) = a$.
By the same argument, $1/\pi_a$ is the expected return time to $a$.

Thus the expected time from $a$ to $b$ and back is
the product of the expected number of times we return to $a$ before reaching $b$
and the expected return time to $a$.
The commute time identity follows
\begin{align}
E_a[T_b] + E_b[T_a] = \frac{1}{\pi_a}\frac{1}{\pr_a(T_b < T_a)} = \Reff C.
\label{eqn:commute}
\end{align}

\section{Bounds}
\subsection{Matthews Method}
We have seen that it is in general very hard
to calculate the cover time of a random walk
on a graph.
The exceptions are symmetric or small graphs.
In lieu of an exact solution, we want to 
bound the cover time.

@@

\begin{theorem}
Let $(X_t)$ be a random walk on a graph with $n$ vertices. Then \label{thm:matthews}
\end{theorem}
\begin{align}
\tcov &\leq \hit \left(1 + \frac{1}{2} + \frac{1}{3} + ... + \frac{1}{n-1} \right). \nonumber
\end{align}

@@

Let $T_k$ be the first time that vertices $\sigma_1, \sigma_2, ..., \sigma_k$
have all been visited.
For ease of notation, set $L_k = X_{T_k}$ to be the last state among 
$\sigma_1, \sigma_2, ..., \sigma_k$ to be visited the first
time they are all visited.

We begin by writing the cover time in a clever way
(similar to the strategy we employed on the cycle graph):
\begin{align}
\tcov &= \E_n[{T_{n-1}}]  \nonumber \\
&= \E_n[T_1 + (T_2 - T_1) + ... + 
(T_k - T_{k-1}) + ... + (T_{n-1} - T_{n-2})] . \nonumber
\end{align}

@@

Since $\sigma$ is a random permutation, the probability that
we visit $\sigma_k$ last is $1/k$.
Formally, $P(L_k = \sigma_k) = 1/k$.

@@

Putting it all together,
\begin{align}
\tcov \leq \hit \left( 1+ \frac{1}{2} + ... + \frac{1}{k} 
+ ... + \frac{1}{n-1} \right). \nonumber
\end{align}

@@

\subsubsection{Balanced Trees}
\cite{LP17} 11.3

@@

@@

\cite{Bo98}
\cite{Gr10}
